\documentclass[10.5pt,a4paper]{article}

% ---------------- Packages ----------------
\usepackage[left=1.4cm,right=1.4cm,top=1.4cm,bottom=1.4cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

% ---------------- Formatting ----------------
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=1pt}
\pagenumbering{gobble}

\titleformat{\section}
  {\bfseries\small}
  {}
  {0pt}
  {}[\titlerule]

% ---------------- Document ----------------
\begin{document}

% ---------------- Header ----------------
\begin{center}
{\Large \textbf{Shamil A}}\\
\vspace{2pt}
\textbf{Full Stack Engineer}\\
\vspace{6pt}

\href{mailto:shamilamiyan@gmail.com}{shamilamiyan@gmail.com}
\;\;|\;\;
+91 97446 76504\\
\vspace{2pt}

\href{https://github.com/your-github}{GitHub}
\;\;|\;\;
\href{https://linkedin.com/in/your-linkedin}{LinkedIn}
\;\;|\;\;
\href{https://your-portfolio.com}{Portfolio}
\end{center}



% ---------------- Summary ----------------
\section*{Summary}
Full Stack Engineer with 2+ years of experience building scalable web applications and backend systems.
Strong expertise in Node.js, TypeScript, Express, MongoDB, and SQL databases, with hands-on experience in
ERP systems, CRM workflows, and AWS cloud deployment. Proven ability to design secure APIs, optimize
performance, and deliver production-ready solutions.

% ---------------- Skills ----------------
\section*{Technical Skills}
\textbf{Frontend:} React.js, Next.js, React Native, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, TypeScript, Python \\
\textbf{Databases:} MongoDB, PostgreSQL, MySQL \\
\textbf{Cloud \& DevOps:} AWS (EC2, Route 53), Nginx, Cloudflare \\
\textbf{Tools:} Git, GitHub, Postman, Figma \\
\textbf{Other:} Redux, JWT, OAuth, Firebase, Zoho Books Integration

% ---------------- Experience ----------------
\section*{Experience}

\textbf{Software Engineer — 3R Creative (Onsite)} \hfill Jun 2025 -- Present
\begin{itemize}
  \item Built a custom ERP system for bullion management covering inventory, sales, purchases, and accounting.
  \item Developed core backend modules including stock registry, metal purity analysis, and automated ledger management.
  \item Integrated Zoho Books for real-time synchronization of invoices, bills, customers, and vendors.
  \item Designed secure REST APIs using Node.js and Express for high-accuracy financial data.
\end{itemize}

\textbf{Full Stack Developer — Raizzify (Remote)} \hfill Jun 2024 -- Jun 2025
\begin{itemize}
  \item Developed a CRM and Admin Panel from scratch using the MERN stack.
  \item Implemented JWT-based authentication and role-based access control.
  \item Optimized backend queries and frontend rendering to improve performance and scalability.
\end{itemize}

% ---------------- Projects ----------------
\section*{Projects}

\textbf{Thiqaf — Multilingual E-commerce Platform} \hfill Jan 2025 -- Present \\
\href{https://github.com/your-github/thiqaf}{GitHub} \;|\;
\href{https://thiqaf.live}{Live}
\begin{itemize}
  \item Built a multilingual (Arabic \& English) e-commerce platform with full RTL support.
  \item Developed using MERN stack with Redux for scalable state management.
  \item Integrated secure payment workflows and optimized backend performance.
\end{itemize}

\textbf{Quotely — White-Label Quotation Platform} \hfill Jan 2025 -- Present \\
\href{https://github.com/your-github/quotely}{GitHub} \;|\;
\href{https://quotely.live}{Live}
\begin{itemize}
  \item Developed a multi-tenant quotation system with dynamic pricing logic.
  \item Implemented subdomain-based architecture for factory-level isolation.
  \item Built reusable white-label components supporting custom branding.
\end{itemize}

% ---------------- Education ----------------
\section*{Education}
\textbf{Bachelor of Computer Applications (BCA)} — Manipal University, Jaipur \hfill Expected 2027

\end{document}
